Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Changes on Sec 2

Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial \red{[explain index n! why do you need to work on a Euclidean domain?]}. Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
\begin{equation}
\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
\end{equation}
In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.

\red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]}

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers. Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.

The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.

\red{[first: lemmae precede theorems. ]}

%
\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are bounded uncorrelated white noises.
% 
\end{myassumption}

@@

By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
\begin{equation}
\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
\end{equation}
considering the Lemma~\ref{lemma:variance}:
\begin{equation}
\nu(z)=  \frac{q^{2}}{12}.
\end{equation}
\end{proof}

@@

>>>>

Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
and assume that there exists a function $FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial. $\mathcal{P}^{n}$ is the space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F \rangle$ is is the space of polynomials with coefficients in $\mathbb{R}\langle I,F \rangle$.
%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
\begin{equation}
\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
\end{equation}
In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.

\red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]} 
\blue{[IB: There is no relationship. We must separate that content in another section?]}

@@

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are bounded uncorrelated white noises.
% 
\end{myassumption}

@@

By definition~\cite{poularikas2000transforms}, the power spectral density of  $\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
\begin{equation}
S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
\end{equation}
considering the Lemma~\ref{lemma:variance}:
\begin{equation}
S_{\nu}(z)=  \frac{q^{2}}{12}.
\end{equation}
\end{proof}

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers. Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.  The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.

%\red{[first: lemmae precede theorems. ]}
